---
title: "Developing Data Products - Week 3"
author: "Nathan Weyer"
date: "10/20/2021"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Initial Slide.

Create a web page presentation using R Markdown that features a plot created with Plotly. Host your webpage on either GitHub Pages, RPubs, or NeoCities. Your webpage must contain the date that you created the document, and it must contain a plot created with Plotly. We would love to see you show off your creativity! 

### Review criteria

The rubric contains the following two questions:

- Does the web page feature a date and is this date less than two months before the date that you're grading this assignment?
- Is the web page a presentation and does it feature an interactive plot that appears to have been created with Plotly?

## Philadelphia Cencus Tracts by Land Area (code)

```{r echo = FALSE, warning=FALSE,message=FALSE,results='hide'}
library(plotly)
library(sf)
Sys.setenv(MAPBOX_TOKEN = 11122223333444)
shape_file_name = file.path("Census_Tracts_2010",
                      "c16590ca-5adf-4332-aaec-9323b2fa7e7d2020328-1-1jurugw.pr6w.shp")
shape_file = st_read(shape_file_name)
```


```{r echo = TRUE, warning=FALSE,message=FALSE,results='hide'}
plot <- ggplot(shape_file,aes(fill=ALAND10,text=NAMELSAD10)) + geom_sf()
plot <- plot + theme_minimal()
plot <- plot + scale_fill_gradient(low="blue",high="red")
plot <- plot + theme(axis.text.x=element_blank())
plot <- plot + theme(axis.text.y=element_blank())
plot <- plot %>% hide_legend() 
ggplotly(plot)
```
## Philadelphia Cencus Tracts by Land Area (map)


```{r echo=FALSE}
ggplotly(plot)
```

## Final Slide

This is a third slide.  It identifies itself as such.
