---
title: "Developing Data Products - Week 4"
author: "Nathan Weyer"
date: "10/24/2021"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Developing Data Products - Week 4 Project

Visualizing Philadelphia Census data using Shiny and Plotly.

## Assignment
Your Shiny Application

- Write a shiny application with associated supporting documentation. The documentation should be thought of as whatever a user will need to get started using your application.

- Deploy the application on Rstudio's shiny server

- Share the application link by pasting it into the provided text box

- Share your server.R and ui.R code on github

The application must include the following:

- Some form of input (widget: textbox, radio button, checkbox, ...)

- Some operation on the ui input in sever.R

- Some reactive output displayed as a result of server calculations

- You must also include enough documentation so that a novice user could use your application.

- The documentation should be at the Shiny website itself. Do not post to an external link.

## Application Overview

- The application is written using R, Shiny, and Plotly.

- The Source is split between cooker.R, server.R, and ui.R

- Data is pre-processed and saved as data.rds

- Application is hosed on RStudio's ShinyApps.io service.

## Operation

* Top Panel contains basic instructions
* Dataset panel allows selection of dataset
  + Age By Sex
  + Education By Sex
* Map Panel displays map of census tracts, which are selectable
* Histogram Panel is loaded when Map Panel item is selected

## Example Page

```{r echo = FALSE, warning=FALSE,message=FALSE}
library(shiny)
library(sf)
library(rjson)
library(stringr)
library(plotly)
library(gridExtra)
data_name = file.path("census_viewer","data.rds")
data = readRDS(data_name)
DataSet <- "Age"
lplot <- plot_ly(data$shape_file,
                         split=~NAMELSAD10,
                         color=reformulate(DataSet),
                         text=~NAMELSAD10,
                         span = I(1),
                         hoveron = "fills",
                         hoverinfo = "text",
                         showlegend=FALSE,
                         source = "A",
                         key=~GEOID10) 
key <- 42101031200
shape_row = data$shape_file[which(data$shape_file$GEOID10 == key),]

geo_idx <- which(colnames(df)=="GEOID10")
mData <- data[[DataSet]][['Male']] 
fData <- data[[DataSet]][['Female']] 
        
mx   <- colnames(mData)[colnames(mData) != 'GEOID10']
xform <- list(categoryorder = "array",categoryarray = mx)
        
my   <- as.numeric(mData[which(mData$GEOID10 == key),!(names(mData) %in% c('GEOID10'))])
fy   <- as.numeric(fData[which(fData$GEOID10 == key),!(names(fData) %in% c('GEOID10'))])
rplot <- plot_ly(mData,x=mx,y=my, type = 'bar', name = 'Male',orientation = 'v')
rplot <- rplot %>% add_trace(y=fy,name="Female")
rplot <- rplot %>% layout(barmode = 'group',xaxis=xform)

subplot(lplot,rplot)
```

## Links