---
title: "Developing Data Products - Week 4"
author: "Nathan Weyer"
date: "10/24/2021"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Developing Data Products - Week 4 Project

Visualizing Philadelphia Census data using Shiny and Plotly.


## Application Overview

* The application is written using R, Shiny, and Plotly.
* The Source is split between cooker.R, server.R, and ui.R
* Data is pre-processed and saved as data.rds
* Application is hosed on RStudio's ShinyApps.io service.

### Operation

* Top Panel contains basic instructions
* Dataset panel allows selection of dataset
  + Age By Sex
  + Education By Sex
* Map Panel displays map of census tracts, which are selectable
* Histogram Panel is loaded when Map Panel item is selected

## Example Page

```{r echo = FALSE, warning=FALSE,message=FALSE}
library(shiny)
library(sf)
library(rjson)
library(stringr)
library(plotly)
library(gridExtra)
data_name = file.path("census_viewer","data.rds")
data = readRDS(data_name)
DataSet <- "Age"
lplot <- plot_ly(data$shape_file,
                         split=~NAMELSAD10,
                         color=reformulate(DataSet),
                         text=~NAMELSAD10,
                         span = I(1),
                         hoveron = "fills",
                         hoverinfo = "text",
                         showlegend=FALSE,
                         source = "A",
                         key=~GEOID10) 
key <- 42101031200
shape_row = data$shape_file[which(data$shape_file$GEOID10 == key),]

geo_idx <- which(colnames(df)=="GEOID10")
mData <- data[[DataSet]][['Male']] 
fData <- data[[DataSet]][['Female']] 
        
mx   <- colnames(mData)[colnames(mData) != 'GEOID10']
xform <- list(categoryorder = "array",categoryarray = mx)
        
my   <- as.numeric(mData[which(mData$GEOID10 == key),!(names(mData) %in% c('GEOID10'))])
fy   <- as.numeric(fData[which(fData$GEOID10 == key),!(names(fData) %in% c('GEOID10'))])
rplot <- plot_ly(mData,x=mx,y=my, type = 'bar', name = 'Male',orientation = 'v')
rplot <- rplot %>% add_trace(y=fy,name="Female")
rplot <- rplot %>% layout(barmode = 'group',xaxis=xform)

subplot(lplot,rplot)
```

## Links

- [Link to Shiny App hosted on Shineyapps.io](https://n6buuk-neeneko.shinyapps.io/census_viewer/)
- [Link to GitHub Repo for project](https://github.com/Neeneko/Coursera-Data-Science/tree/main/Developing%20Data%20Products/Week%204)
- [Link to Census Tracks Shapefile](https://www.opendataphilly.org/dataset/census-tracts)
- Data sourced from [Census Reporter](https://censusreporter.org/) website.